---
title: "figure_2"
author: "vb"
format: html
editor: visual
---

## Figure 2 - seeds and voronois

### functions and library

```{r}

#libraries
library(EBImage)
library(imager)
library(imagerExtra)
library(magick)

library(tidyverse)
library(pipeR)

#percentage_crop

#manual_crop

#get_intermediate_images

#get_features_BF_for_mini

#do_tesselation

#prepare_colors

#cook_plot_new

```

### set parameters and input

```{r}

#individual_filpath_C08_221207_BF

#pixset_dims


```

### no crop seeds

```{r}
#| fig-width: 8.136
#| fig-height: 5.992

individual_filpath_C08_221207_BF %>%  
  get_intermediate_images(.,
    crop_percentage = my_crop_percentage,
    my_isoblur = my_isoblur,
    my_k = my_k, 
    my_ws = my_ws,
    my_clean = my_clean,
    my_grow = my_grow, 
    my_shrink = my_shrink) %>% 
  pluck("shrink") %>% 
  get_features_BF_for_mini() %>% 
  ggplot(aes(x  = x, y = -y))+
  geom_point(size = 2, color = "darkgreen", alpha = 0.6)+
  theme_void()

```

### cropped seeds

```{r}
#| fig-width: 8.285
#| fig-height: 7.1

individual_filpath_C08_221207_BF %>%  
  get_intermediate_images(.,
    crop_percentage = my_crop_percentage,
    my_isoblur = my_isoblur,
    my_k = my_k, 
    my_ws = my_ws,
    my_clean = my_clean,
    my_grow = my_grow, 
    my_shrink = my_shrink)
  pluck("shrink") %>% 
  EBImage::Image() %>% 
  manual_crop(crop_y_left = 0.84,
              crop_y_right = 0.03,
              crop_x_low = 0.84,
              crop_x_up = 0.01) %>% 
  get_features_BF_for_mini() %>% 
  ggplot(aes(x  = x, y = -y))+
  geom_point(size = 20, color = "darkgreen", alpha = 0.6)+
  theme_void()

```

### voronoi no crop (higher resolution also for screenshot)

```{r}
#| fig-width: 24.408
#| fig-height: 17.976

individual_filpath_C08_221207_BF %>%  
  get_intermediate_images(.,
    crop_percentage = my_crop_percentage,
    my_isoblur = my_isoblur,
    my_k = my_k, 
    my_ws = my_ws,
    my_clean = my_clean,
    my_grow = my_grow, 
    my_shrink = my_shrink)
  pluck("shrink") %>% 
  get_features_BF_for_mini() %>% 
  do_tesselation(well_name = "C08", 
                 boundary_box = c(0, pixset_dims %>% nth(1), 
                                0, pixset_dims %>%  nth(2))) %>% 
  prepare_colors(input_image = "BF") %>% 
  cook_plot_new(boundary_rectangle = c(0, pixset_dims %>% nth(1), 
                                -(pixset_dims %>%  nth(2)) , 0),
                print_well_label = FALSE,
                color_me_white = TRUE,
                color_non_white = 8,
                my_max_radius = 1000,
                my_linewidth = 3,
                plot_points = FALSE) 
  

```

### colored image for no crop and screnshot

```{r}
#| fig-width: 24.408
#| fig-height: 17.976

individual_filpath_C08_221207_BF %>%  
  get_intermediate_images(.,
    crop_percentage = my_crop_percentage,
    my_isoblur = my_isoblur,
    my_k = my_k, 
    my_ws = my_ws,
    my_clean = my_clean,
    my_grow = my_grow, 
    my_shrink = my_shrink)
  pluck("shrink") %>% 
  get_features_BF_for_mini() %>% 
  do_tesselation(well_name = "C08", 
                 boundary_box = c(0, pixset_dims %>% nth(1), 
                                0, pixset_dims %>%  nth(2))) %>% 
  prepare_colors(input_image = "BF") %>% 
  cook_plot_new(boundary_rectangle = c(0, pixset_dims %>% nth(1), 
                                -(pixset_dims %>%  nth(2)) , 0),
                print_well_label = FALSE,
                color_me_white = FALSE,
                color_non_white = 8,
                my_max_radius = 1000,
                my_linewidth = 0.1,
                plot_points = FALSE,
                with_legend = TRUE) 
  

```

#### my used function in this file

```{r}

#qmd code copied to R file
#NCmisc::list.functions.in.file(here::here("prepration.R"))

```

all functions and packages in this files:

\$.GlobalEnv \[1\] "cook_plot_new" "do_tesselation"\
\[3\] "get_features_BF_for_mini" "manual_crop"\
\[5\] "prepare_colors"

\$`character(0)` \[1\] "get_intermediate_images"

\$`package:base` \[1\] "c" "library"

\$`package:dplyr` \[1\] "nth"

\$`package:EBImage` \[1\] "Image"

\$`package:ggplot2` \[1\] "aes" "geom_point" "ggplot" "theme_void"

\$`package:purrr` \[1\] "pluck"
